---
title: "Assurance of Learning"
subtitle: "2023/2024 academic year"
date: "`r Sys.Date()`"
format:
  pdf:
    include-in-header:
      - "suport/aol.template.tex"
classoption: a4paper
always_allow_html: yes
editor: visual
fontsize: 10pt
title-block-style: none
project:
  output-dir: quarto/
---

```{r setup, include=FALSE, echo = FALSE}
      load("all_data.Rdata")
      knitr::opts_chunk$set(echo = TRUE, dev="cairo_pdf")
      library(tidyverse)
      library(extrafont)
      library(ggthemes)
      library(scales)
      library(flextable)
      library(officer)
```

\newpage
\pagestyle{plain}

# About {.unnumbered}

This document offers a detailed account of the Assurance of Learning (AoL) developments and key changes for the 2023/2024 academic year. It outlines the processes and methodologies implemented during this period, ensuring clarity and transparency in our approach.

Furthermore, it provides a comprehensive analysis of the results from the 2023/2024 academic year assessments, highlighting significant outcomes and findings that are essential for ongoing improvement.

Based on the insights gathered, the document proposes recommendations for enhancements for the three year cycle that will start in 2024/2025. These recommendations are designed to boost the effectiveness of the AoL process and align with our broader academic objectives, aiming to continuously improve the quality of education provided.

\newpage

\hypersetup{
  colorlinks = true,
  linkcolor = black,  % This makes internal links black
  urlcolor = black,   % This makes URL links black
  citecolor = black   % This makes citation links black
}

\tableofcontents

\newpage

\pagestyle{plain}

# Executive summary

\newpage

# Assurance of Learning

**Assurance of Learning** (AoL) is a continuous improvement process designed to evaluate whether students are effectively acquiring the competencies and skills that their programs intend to impart, and to adjust pedagogical practices accordingly. The goal of AoL is not to replace existing quality control mechanisms[^1] but to enhance them.

[^1]: [Nova SIMAQ](https://www.unl.pt/en/nova/nova-simaq) - NOVA’s Internal Quality Monitoring and Evaluation System. It is aligned with the University’s Strategic Plan, covering all its activities and ensuring the involvement of all stakeholders (internal and external). It aims at the continuous improvement of NOVA’s Quality, responding to the legal requirement of implementing its own Quality assurance systems.

Initially, quality control in education primarily focused on student satisfaction, course instructors' self-assessments, and adherence to pre-defined procedures. However, there was no explicit, systematic process for assessing the actual knowledge and competency acquisition by students. Such assessments were indirectly made by faculty and the academic director, based on the assumption that if individual course subjects aligned with program goals, and students were passing these courses, they would necessarily be acquiring the expected competencies and skills. This assumption underpinned the previous AoL approach, which relied on instructors' self-assessments and peer reviews. While this approach was supported by the faculty's and academic director's commitment to excellence and student development, it lacked direct and systematic evidence of actual competency acquisition.

The Assurance of Learning process seeks to address this gap by providing a more structured and evidence-based assessment framework that complements the existing quality controls, ensuring a more robust and transparent measure of educational outcomes.

## Goals

The primary objective of the Assurance of Learning (AoL) is to ensure that students meet predefined program-level learning outcomes and to foster continuous quality improvement within academic programs. To achieve this, AoL first establishes specific Learning Outcomes (LOs) for each course. It then employs a predefined sampling strategy to assess the extent to which these outcomes have been achieved.

Assessment occurs at the individual course level, with each course mapped against the overall program LOs to measure its contribution. Additionally, indirect measures of student learning are incorporated through surveys conducted by the Career Placement department, which gathers feedback from corporate recruiters, also alumni who have graduated within the last three years are surveyed. They are asked to rate, on a Likert scale, their agreement with statements describing their proficiency in each LO.

This data triangulation strategy aims to create an interactive process where the acquisition of each LO is measured. The process identifies and addresses gaps, enhancing the educational experience.

Currently, we are in a development phase focused on ensuring that LOs are a central consideration as faculty members develop syllabi. Faculty are expected to integrate LOs into their course materials, planning, and assessment practices. Additionally, any gaps identified in previous assessments are addressed by the Academic Directors during the program curriculum design and individual syllabus development phases.

It is also important to recognize that program LOs are not static; they evolve over time to reflect changing student and market needs. Eventually, these LOs will need to be revisited and revised. In this context, the role of AoL is to ensure coherence across the program and course structures, swiftly incorporating any revisions to the LOs into the program structure and course content, and ensuring that outdated LOs are fully replaced by the new standards.

# Structure

To maintain coherence with both the school's ethos and the specific objectives of each program, the Assurance of Learning at Nova SBE is structured using a hierarchical approach (@fig-design). This structured approach begins with the core school values and cascades through program objectives down to specific learning outcomes.

![Assurance of Learning design](figures/design.svg){#fig-design fig-align="center"}

The process begins with our foundational school values and their reflection in the specific program objectives. These objectives are then mapped to LOs, ensuring that the core measures of the AoL process not only reflect Nova SBE's values but also effectively meet desired educational and professional standards.

Further, we meticulously select Learning Outcomes for each academic year and identify precise moments within courses to assess these outcomes. This selection process is crucial for gathering relevant data and ensuring that the assessments accurately reflect the educational impact on our students.

This leads into our yearly evaluation cycle, where we collect and analyze data to measure how well these outcomes are being achieved. This cycle is not only vital for continuous improvement but also ensures that our programs adapt to evolving educational and industry standards.

## School Values {#sec-SV}

We initiated our approach by focusing on our core values, which are integral to everything we do. As such, it's essential that the learning outcomes of our programs align with these foundational principles:

-   Rigor
-   Impact
-   Worldliness
-   Vanguardism
-   Connectivity

This alignment ensures not only coherence with our school’s ethos but also facilitates a structured and recognizable framework across all courses. This framework supports an easier understanding and implementation of the Assurance of Learning (AoL) process.

Building on this foundation, we analyzed the current program objectives submitted to A3ES, the national accreditation agency. These objectives were crafted with Nova SBE’s values in mind. Our analysis revealed a common value matrix that intersects all programs and should be mirrored in the programs' Learning Outcomes (LOs). We also uncovered a latent structure that underlies the specific objectives of each program.

Leveraging these shared values and the underlying structure common to all programs, we have developed six Learning Outcomes (LOs) for each program, ensuring that our educational goals are both ambitious and aligned with our institutional values.

## Program Learning Outcome structure {#sec-PLOS}

For each program, six learning outcomes have been established:

-   Three are program-specific, meticulously designed to reflect the unique characteristics and educational objectives of each individual program.
-   Three are universal, shared across all school programs, fostering a cohesive educational experience that embodies Nova SBE's ethos.

This dual-layered framework not only captures the unique identity and specific learning outcomes of each program but also integrates Nova SBE's core values and DNA into every facet of our curriculum. This approach ensures that our overarching values are consistently represented across all program offerings, aligning individual program objectives with the broader institutional goals.

### Specific Learning Outcomes

The three specific learning outcomes differ from course to course at Nova SBE, yet they share a consistent thread that aligns with the school’s core values. This thread not only unites all courses but also shapes how students approach their educational and personal development within the institution.

Accordingly, the specific learning outcomes for each course are strategically defined as follows:

-   **I - Context Understanding**: Students develop a nuanced understanding of the broader context surrounding the subject area. This encompasses comprehending the environmental, economic, social, and technological factors that impact the field, equipping students with the ability to assess and interpret the dynamics that influence their studies.
-   **II - Tool Application**: Students achieve proficiency in applying specialized tools and techniques learned during the course. This outcome focuses on the practical application of these tools, ensuring that students can effectively employ them in real-world situations, thereby bridging the gap between theoretical knowledge and practical implementation.
-   **III - Theory Application**: Students are skilled at translating theoretical concepts into practical solutions. This involves applying academic theories to real-life challenges, demonstrating a deep understanding of how theoretical frameworks can be utilized to solve concrete problems.

These outcomes are crafted to ensure that while each course maintains its unique focus and depth, the overall educational experience at Nova SBE remains consistent, integrated, and aligned with the school's values. This approach not only reinforces the relevance of each course within the broader educational aims of Nova SBE but also enhances the students’ ability to apply their learning in varied and complex real-world scenarios.

### Universal Learning Outcomes

Nova SBE is committed to cultivating professionals who embody a proactive 'go-get-it' attitude. We strive to develop individuals who engage in assertive and effective teamwork, possess the skills to both lead and collaborate, and recognize that their learning journey extends far beyond the classroom. With the mindset and tools to ensure continuous personal and professional growth, our students are prepared to make lasting impacts.

Another key aspect that defines Nova SBE's ethos and internal culture is its commitment to having a positive impact. In line with this, during the academic year of 2022/2023, we introduced an additional Learning Outcome, LO VI, focused specifically on the dimensions of positive impact and sustainability. This new LO underscores Nova SBE's dedication to instilling these crucial values in its students, ensuring that they not only succeed in their careers but also contribute positively to society and the environment.

Accordingly, the shared learning outcomes have been defined to reflect these ambitions:

-   **IV - Interpersonal and Teamwork Skills**: Students will demonstrate effective interpersonal and communication skills, fostering productive teamwork and the capacity to pursue collaborative efforts successfully.

-   **V - Intellectually Curious and Autonomous**: Students will develop analytical, critical thinking, and problem-solving skills that facilitate lifelong learning and autonomous professional development.

-   **VI - Sustainable Values for Positive Impact**: Students will gain a holistic understanding of sustainable business and economic models, applying ethical, social, and environmental values to drive positive and transformative influences within projects and organizations.

These outcomes ensure that our graduates not only meet the current standards of professional excellence but are also equipped to adapt and thrive in an ever-changing global landscape.

## Courses and Program Learning Outcomes

At the start of the Assurance of Learning process in 2021/2022, Learning Outcomes were carefully mapped to each program's mandatory courses and validated by Academic Directors to ensure every course supported the overall program goals. These mappings were rigorously confirmed for accuracy and relevance. Following any changes to mandatory courses—most notably the BSc restructuring in 2023/2024—the new courses were re-mapped and the updated maps were validated by Academic Directors.

Starting in the 2023/2024 academic year, only two Learning Outcomes will be directly assessed each year—one specific to the program and one universal.

## Defining the Learning outcomes

For each learning goal, three proficiency levels were defined based on [Bloom's Taxonomy](https://en.wikipedia.org/wiki/Bloom's_taxonomy), structured as follows:

-   **Developing**: The student is aware of and recognizes the importance of the competencies and skills defined by the Learning Outcome (LO).
-   **Proficient**: The student can apply the competencies and skills defined by the LO in a limited capacity.
-   **Expert**: The student has developed a deep knowledge and understanding of the competencies and skills defined by the LO and can apply them autonomously in various contexts beyond those explicitly taught in the program.

## Assessing the Learning Outcomes {#sec-ALS}

For the 2022/2023 cycle, we began using three distinct data sources to assess learning outcomes (@fig-data). To ensure consistency and clarity, the results from all sources are consolidated into a qualitative scale (A, B, C, F), providing an intuitive overview of performance. This section outlines the analysis process for each data source.

![Assessment data sources](figures/LO_Assessment.svg){#fig-data fig-align="center"}

Direct measures assess student learning by evaluating real work—like tests, presentations, or projects—that align with course objectives (@fig-data). They provide clear evidence of student skills and help validate our curriculum while highlighting areas that need improvement.

Direct measures provide an objective snapshot of student learning through tests, projects, and presentations. However, they capture only a single point in time, and differences in course difficulty mean that systemic issues only emerge when data is collected over several years. This long-term approach helps us understand learning trends and curriculum effectiveness.

Indirect measures, on the other hand, reveal how students, alumni, and employers perceive student competencies. For the 2023/2024 cycle, we have two years of indirect measure data. Tools like alumni and employer surveys show how well students develop the desired skills. Employer feedback is especially valuable because it offers an external view of how education meets real-world demands.

While indirect measures don’t assess student learning directly, they provide a broader picture of a program’s impact. They complement direct measures by ensuring that the curriculum is both academically rigorous and aligned with industry needs.

Combining both direct and indirect measures gives us a well-rounded view of educational effectiveness. This approach reduces bias, improves reliability, and helps us identify strengths and areas for improvement in our programs, ensuring our educational strategies meet both academic and professional standards.

### Direct measures

After mapping how each course contributes to the program’s defined Learning Outcomes (LOs), and with the assistance of the Academic Director, courses to be assessed were selected. For each chosen course, the professor responsible was directly contacted to help identify the assessment moment that best captures the relevant LO. Options for these assessment moments include:

-   Exam
-   Mid-term
-   Term-paper
-   Group project
-   Specific exam question
-   Peer assessment

By integrating the measurement of Learning Outcomes into existing assessment formats, we aim to minimize disruption to the schedules of both professors and graders. Additionally, as the awareness of course learning outcomes becomes more ingrained in all parties involved, we anticipate a natural evolution where course assessments more effectively reflect and measure the intended outcomes.

#### Defining targets

Assessment moments will produce grades ranging from 0 to 20. For grading systems that do not adhere to this format, grades will be proportionally converted to this scale. To align these grades with the Assurance of Learning (AoL) goals, we have categorized them into three brackets:

-   **Below Target**: Grades below 12, indicating that the student has either failed or barely passed the course.
-   **On Target**: Grades between 12 and 16, signifying satisfactory to good performance.
-   **Above Target**: Grades above 16, denoting excellent performance.

To mitigate the potential for grade inflation and avoid it as an incentive, we have chosen to use the Total Percentage of Grades On Target and Above Target (TTAT) as the primary indicator. This metric, representing the combined percentage of grades that are On Target and Above Target, reflects the proportion of students achieving a passing grade in the assessment.

#### Evaluating the results {#sec-EvDirect}

To determine the extent to which the Learning Outcomes (LOs) are being achieved, the Total Percentage of Grades On Target and Above Target (TTAT) will be assessed according to the following scale:

-   **A**: More than 90% TTAT - LO objectives fully achieved.
-   **B**: Between 80% and 90% TTAT - LO objectives achieved.
-   **C**: Between 60% and 80% TTAT - LO objectives insufficiently achieved.
-   **F**: Below 60% TTAT - LO objectives not achieved.

This scale ensures a clear and measurable indicator of student performance relative to the set learning objectives.

::: {.callout-note appearance="simple"}
Learning Outcomes that receive an 'F' rating will be reassessed in the following academic year during the same course and assessment moment, even if no assessment was originally planned for that LO. Then, in academic year n+2, if the LO still receives an '**F**' or '**C**' rating, it will be reassessed again in a different course. Similarly, LOs rated as '**C**' will be reassessed in a different course in the following academic year, with an additional assessment in year n+2 only if they again receive a '**C**' or '**F**' rating.
:::

### Indirect measures

Indirect measures at Nova SBE utilize statement-based surveys where participants rate their agreement with statements that describe mastering the competencies of each Learning Outcome (LO). Administered biannually, these surveys are designed to capture a comprehensive overview of the alumni and employers' perspectives. Alumni surveys are typically integrated with end-of-program evaluations, while employer surveys are conducted during annual career fairs to ensure high participation rates and relevance. This method allows for the continual assessment of all Learning Outcomes each year, providing a consistent and reliable flow of feedback to inform program enhancements.

#### Alumni surveys: {#sec-alumnisurv}

The alumni surveys are comprised of straightforward, statement-based questionnaires in which recently graduated alumni rate, on a Likert scale from 1 to 6, their agreement with statements describing their achievement of the expert-level for each Learning Outcome (LO).

This self-assessment serves as an indirect method for evaluating each LO, offering insights into the effectiveness with which the Learning Outcomes are being realized. The surveys are administered twice annually and are combined with other end-of-program questions that are designed to evaluate additional quality aspects of the programs.

Given that this is an indirect measure requiring minimal time commitment from survey participants, it contrasts with the more targeted, direct LO assessments where only a sample of LOs is evaluated each year (four cycle assessments, plus additional reassessments as needed). Consequently, this method enables the comprehensive assessment of all LOs in every annual cycle.

#### Employers surveys: {#sec-employsurv}

Like the alumni surveys, the employers' surveys consist of statement-based questionnaires. In these surveys, employers rate, on a Likert scale from 1 to 6, their agreement with statements that describe how well they believe the alumni have achieved the expert-level for each Learning Outcome (LO).

This method serves as an indirect way to evaluate each LO, providing insights into the practical effectiveness of the Learning Outcomes as perceived by employers. These surveys are conducted twice a year and are integrated with other queries designed to assess additional quality dimensions of the programs from an employer’s perspective.

Like the alumni surveys, this is an indirect method requiring minimal time commitment from the participants, allowing for a comprehensive assessment of all LOs in each annual cycle. To maximize efficiency and ensure a high volume of responses, the surveys are conducted in person during the two career fairs held annually at Nova SBE's campus. Recruiters were initially asked to specify from which degree programs they recruit graduates. Subsequently, they were directed to complete surveys pertaining specifically to those programs.

#### Defining targets:

The indirect measures utilized in the surveys involve a Likert scale from 1 to 6, where respondents indicate their agreement with statements that assess the mastery of each Learning Outcome (LO). To align these responses with the Assurance of Learning (AoL) goals, we categorize them into three distinct performance brackets:

-   **Below Target**: Responses below 4, indicating that the perceived mastery of competencies is inadequate or just below satisfactory.
-   **On Target**: Responses between 4 and 5.5, signifying that the mastery of competencies is viewed as satisfactory to good.
-   **Above Target**: Responses of 5.5 or higher, denoting excellent perceived mastery of competencies.

To mitigate the potential for bias and ensure a balanced evaluation, we utilize the Total Percentage of Responses On Target and Above Target (TTAT) as the primary indicator. This metric reflects the combined percentage of responses falling within the On Target and Above Target categories and provides a clear measure of how well students believe they have achieved and can apply the program's Learning Outcomes in real-world contexts.

#### Evaluating the results:

Similarly to the direct measures, the evaluation of indirect measures also uses the Total Percentage of Responses On Target and Above Target (TTAT) to determine the extent to which the Learning Outcomes (LOs) are being achieved. For a matter of convenience and to maintain coherence across different types of assessments, the responses are assessed using the same thresholds as those applied in direct measures:

-   **A**: More than 90% TTAT - LO objectives fully achieved.
-   **B**: Between 80% and 90% TTAT - LO objectives substantially achieved.
-   **C**: Between 60% and 80% TTAT - LO objectives insufficiently achieved.
-   **F**: Below 60% TTAT - LO objectives not achieved.

This approach ensures that both direct and indirect measures are aligned, providing a consistent and comprehensive assessment of student performance relative to the set learning objectives.

## Yearly assessment cycle

The Yearly Assessment Cycle is a structured, continuous process designed to evaluate and enhance the effectiveness of our educational programs. This cycle ensures that we consistently monitor, analyze, and improve the learning outcomes and overall quality of education at Nova SBE. The cycle follows the [PDCA (Plan-Do-Check-Act)](https://en.wikipedia.org/wiki/PDCA) methodology, a proven framework for continuous improvement.

The Yearly Assessment Cycle is an ongoing process, fostering a culture of continuous improvement. Each iteration of the cycle builds on the previous one, incorporating new insights and evolving to meet the changing needs of students and the industry. By maintaining this dynamic approach, we ensure that Nova SBE remains at the forefront of educational excellence.

The key stages of the cycle are:

### Select Learning Outcomes to Assess

**Check**: The first step in the cycle involves selecting the specific Learning Outcomes (LOs) that will be assessed during the year. This selection is guided by the need to cover different LOs systematically over time, ensuring a comprehensive evaluation of all program objectives. By rotating the focus of assessment, we ensure that each LO is thoroughly examined and validated periodically. Additionally, any LOs and assessment moments flagged for reassessment in previous cycles will be included to address any identified gaps and verify improvements.

### Collect Measures

**Check**: In this stage, we gather data through various direct and indirect measures. Direct measures may include exams, projects, and presentations that provide tangible evidence of student competencies. Indirect measures involve feedback from alumni and employers through surveys, which offer insights into the perceived effectiveness of the educational programs. This combination of data sources helps to create a well-rounded understanding of how well students are meeting the LOs.

### Analyze Data

**Act**: Once the data is collected, it is analyzed to identify trends, strengths, and areas needing improvement. This analysis involves comparing the collected data against predefined benchmarks and standards. Based on the defined criteria, data points are classified into "Below Target," "On Target," or "Above Target" categories. By calculating the total percentage of On Target and Above Target (TATT), a qualitative evaluation of A, B, C, or F is assigned to the assessed LO. This process is performed for both direct measures and indirect measures, ensuring a comprehensive understanding of the extent to which the LOs are being achieved and identifying any gaps in the curriculum or instructional methods.

### Results and Recommendations

**Plan**: Based on the data analysis, we identify potential structural flaws in both the curricula and the courses themselves. By combining the evaluation and reevaluation of direct measures with indirect measures, we aim to understand if an issue is systematic or focused on a specific course or just a particular assessment moment. Based on this understanding, we select LOs and assessment moments for reassessment in the coming yearly cycles and generate reports that pinpoint where the Academic Directors need to focus their attention for continuous improvement of the programs.

These findings are shared with the academic directors, relevant faculty and program administrators to guide their decision-making processes.

### Implement changes

**Do**: The final stage of the cycle involves implementing the recommended changes. Based on the identified issues, the academic directors of each program will meet with the relevant faculty to pinpoint root causes and develop improvement plans. If an issue is found to be systemic, the academic directors will review and potentially revise the curricula to address the broader concerns. This critical step ensures that the insights gained from the assessment process are translated into practical, actionable improvements. By closing the loop, we continually refine and elevate our educational offerings, ensuring they align more closely with Nova SBE's values and objectives. This iterative process fosters a culture of continuous improvement, enabling us to adapt and respond to evolving educational needs and industry standards.

# BSc in Economics

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 1

```

## Program objectives

Based on Nova SBE's core values, the program objectives, which were previously defined and submitted to A3ES and international accreditation agencies, have been systematically mapped. This mapping process, as described in @sec-SV, ensures alignment with our institutional ethos and educational goals for the program `{r} print.program.b(c)`.

The @tbl-VO1, below, provides a detailed overview of how these objectives correspond to the learning outcomes, illustrating the integration of Nova SBE’s values into our educational framework:

::: {#tbl-VO1}
```{r echo=FALSE, fig.align='center', out.width="95%"}

VO_table(c)

```

Nova SBE's values and Program objectives for the `{r} print.program.b(c)`
:::

## Learning Outcomes

After evaluating the Program Objectives and their alignment with Nova SBE's core values, and considering the Learning Goals structure outlined in the @sec-PLOS, we have defined the following **Learning Outcomes** for the program `{r} print.program.b(c)`, as detailed in the @tbl-LO1.

::: {#tbl-LO1}
```{r echo=FALSE, fig.align='center', , out.width="98%"}

LO_table(c)

```

Program Learning Outcomes for the `{r} print.program.b(c)`
:::

These Learning Outcomes are described according to the three levels of proficiency defined in @sec-PLOS: Developing, Proficient, and Expert. @tbl-PLO1, below, outlines the levels of proficiency for the Learning Outcomes in the `{r} print.program.b(c)` program. Each Learning Outcome is mapped across three proficiency levels—Developing, Proficient, and Expert—detailing the competencies students are expected to demonstrate as they progress through the program.

::: {#tbl-PLO1}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Prof_table(c)

```

Levels of Proficiency for Learning Outcomes in the `{r} print.program.b(c)`
:::

The defined Learning Outcomes contribute to achieving the program's pre-defined objectives, as detailed in the @tbl-OO1 of the [Appendix 1.A](#sec-app1). Additionally, the specific contributions of individual courses to each Learning Outcome, along with the corresponding levels of proficiency achieved, are detailed in @tbl-CO1, located in [Appendix 1.A](#sec-appcourse1).

## 2023/2024 Academic year

For the academic year 2023/2024, in accordance with the procedure defined in @sec-ALS, the following courses were selected for the Learning Outcomes (LO) assessment process for the `{r} print.program.b(c)` program. The details of these courses and their respective contributions to the LO assessment are presented in the @tbl-ConifgLO1 below.

::: {#tbl-ConifgLO1}
```{r echo=FALSE, fig.align='center', out.width="95%"}

config_table(c)

```

2023/2024 academic year Selected Learning Outcomes and respective courses for the `{r} print.program.b(c)`
:::

## Results

The results for the `{r} print.program.b(c)` for the academic year of 2023/2024, were the following.

### Direct Measures

#### Learning Outcome I:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'I'
e <- FALSE
f <- 1118

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome IV:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'IV'
e <- FALSE
f <- 1462

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome II - Reassessment 1:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'II'
e <- TRUE
f <- 1310
  
data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome II - Reassessment 2:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'II'
e <- TRUE
f <- 1313
  
data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome III - Reassessment:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'III'
e <- TRUE
f <- 1124

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome V - Reassessment:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'V'
e <- TRUE
f <- 1312

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome VI - Reassessment:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'VI'
e <- TRUE
f <- 1463

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```


### Indirect Measures

#### Alumni surveys:

Below, @tbl-KPIalumni1 provides a summary of the alumni survey results for the `{r} print.program.b(c)` during the 2023/2024 academic year. The scores, based on responses from `{r} print.alumni.num(c)` alumni, are reported on an A, B, C, F scale, as outlined in @sec-alumnisurv.

::: {#tbl-KPIalumni1}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Alumni_table (c)

```

Results of the alumni surveys for the `{r} print.program.b(c)`
:::

#### Employers surveys:

The results of the employer survey for the `{r} print.program.b(c)` in the 2023/2024 academic year are summarized in @tbl-KPIemploy1. Based on feedback from `{r} print.employers.num(c)` employers, the scores are presented on an A, B, C, F scale, as detailed in @sec-employsurv.

::: {#tbl-KPIemploy1}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Employer_table (c)

```

Results of the employer surveys for the `{r} print.program.b(c)`
:::

### Integrated assurance overview {#sec-totalint1}

The table below, @tbl-Total1, presents the integrated results for the program `{r} print.program.b(c)`, combining both direct and indirect measures of assessment. Data was triangulated as described in @sec-ALS, ensuring a comprehensive evaluation of the learning outcomes.

::: {#tbl-Total1}
```{r echo=FALSE, fig.align='center', out.width="98%"}

KPI_total_table (c)

```

Integrated direct and indirect measures results for the `{r} print.program.b(c)`
:::

By integrating the various dimensions, including the indirect survey-based data from the 2023/2024 academic year, along with the reassessments and regular assessments from 2023/2024, we gain a comprehensive overview of the learning outcomes for the `{r} print.program.b(c)`.


## Outcomes and Recommendations

Drawing on the integrated results presented in @sec-totalint1, we have identified key insights that underpin our strategies for ongoing evaluation and enhancement:

- **Learning Outcome I** - *Applies a broad understanding of national and international economic contexts, including social, legal, historical, and political factors, to develop comprehensive economic analyses and strategies*  - **Course 1118 - Principles of Macroeconomics**: Improvement plan to be developed. 

- **Learning Outcome III** - *Understands the key theories and practices in core areas of economic science and acquire the ability to apply these to actual situations*  - **Course 1124 - Economic history**: Course instructor no longer at Nova SBE. New course instructor should be made aware of potential issues. 

- **Learning Outcome V** - *Utilizes analytical, critical thinking, and problem-solving skills to navigate challenges and enable lifelong learning within teams and organizations.* – **Course: 1312 - Data Analysis and Probability**: Improvement plan to be developed.

- **Learning Outcome VI** - *Leverages a deep understanding of sustainability in business and economics to drive ethical transformations and positive outcomes across organizational and project contexts*. – **Course: 1463 - Ethics**: Improvement plan to be developed.


# BSc in Management

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 2

```

## Program objectives

Based on Nova SBE's core values, the program objectives, which were previously defined and submitted to A3ES and international accreditation agencies, have been systematically mapped. This mapping process, as described in @sec-SV, ensures alignment with our institutional ethos and educational goals for the program `{r} print.program.b(c)`.

The @tbl-VO2, below, provides a detailed overview of how these objectives correspond to the learning outcomes, illustrating the integration of Nova SBE’s values into our educational framework:

::: {#tbl-VO2}
```{r echo=FALSE, fig.align='center', out.width="95%"}

VO_table(c)

```

Nova SBE's values and Program objectives for the `{r} print.program.b(c)`
:::

## Learning Outcomes

After evaluating the Program Objectives and their alignment with Nova SBE's core values, and considering the Learning Goals structure outlined in the @sec-PLOS, we have defined the following **Learning Outcomes** for the program `{r} print.program.b(c)`, as detailed in the @tbl-LO2.

::: {#tbl-LO2}
```{r echo=FALSE, fig.align='center', , out.width="98%"}

LO_table(c)

```

Program Learning Outcomes for the `{r} print.program.b(c)`
:::

These Learning Outcomes are described according to the three levels of proficiency defined in @sec-PLOS: Developing, Proficient, and Expert. @tbl-PLO2, below, outlines the levels of proficiency for the Learning Outcomes in the `{r} print.program.b(c)` program. Each Learning Outcome is mapped across three proficiency levels—Developing, Proficient, and Expert—detailing the competencies students are expected to demonstrate as they progress through the program.

::: {#tbl-PLO2}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Prof_table(c)

```

Levels of Proficiency for Learning Outcomes in the `{r} print.program.b(c)`
:::

The defined Learning Outcomes contribute to achieving the program's pre-defined objectives, as detailed in the @tbl-OO2 of the [Appendix 2.A](#sec-app2). Additionally, the specific contributions of individual courses to each Learning Outcome, along with the corresponding levels of proficiency achieved, are detailed in @tbl-CO2, located in [Appendix 2.B](#sec-appcourse2).

## 2023/2024 Academic year

For the academic year 2023/2024, in accordance with the procedure defined in @sec-ALS, the following courses were selected for the Learning Outcomes (LO) assessment process for the `{r} print.program.b(c)` program. The details of these courses and their respective contributions to the LO assessment are presented in the @tbl-ConifgLO2 below.

::: {#tbl-ConifgLO2}
```{r echo=FALSE, fig.align='center', out.width="95%"}

config_table(c)

```

2023/2024 academic year Selected Learning Outcomes and respective courses for the `{r} print.program.b(c)`
:::

## Results

The results for the `{r} print.program.b(c)` for the academic year of 2023/2024, were the following.

### Direct Measures

#### Learning Outcome I:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'I'
e <- FALSE
f <- 1218

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome IV:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'IV'
e <- FALSE
f <- 1462

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome II - Reassessment 1:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'II'
e <- TRUE
f <- 1310
  
data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome II - Reassessment 2:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'II'
e <- TRUE
f <- 1313
  
data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome V - Reassessment:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'V'
e <- TRUE
f <- 1312

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```


### Indirect Measures

#### Alumni surveys:

Below, @tbl-KPIalumni2 provides a summary of the alumni survey results for the `{r} print.program.b(c)` during the 2023/2024 academic year. The scores, based on responses from `{r} print.alumni.num(c)` alumni, are reported on an A, B, C, F scale, as outlined in @sec-alumnisurv.

::: {#tbl-KPIalumni2}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Alumni_table (c)

```

Results of the alumni surveys for the `{r} print.program.b(c)`
:::

#### Employers surveys:

The results of the employer survey for the `{r} print.program.b(c)` in the 2023/2024 academic year are summarized in @tbl-KPIemploy2. Based on feedback from `{r} print.employers.num(c)` employers, the scores are presented on an A, B, C, F scale, as detailed in @sec-employsurv.

::: {#tbl-KPIemploy2}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Employer_table (c)

```

Results of the employer surveys for the `{r} print.program.b(c)`
:::

### Integrated assurance overview {#sec-totalint2}

The table below, @tbl-Total2, presents the integrated results for the program `{r} print.program.b(c)`, combining both direct and indirect measures of assessment. Data was triangulated as described in @sec-ALS, ensuring a comprehensive evaluation of the learning outcomes.

::: {#tbl-Total2}
```{r echo=FALSE, fig.align='center', out.width="98%"}

KPI_total_table (c)

```

Integrated direct and indirect measures results for the `{r} print.program.b(c)`
:::

By integrating the various dimensions, including the indirect survey-based data from the 2023/2024 academic year, along with the reassessments and regular assessments from 2023/2024, we gain a comprehensive overview of the learning outcomes for the `{r} print.program.b(c)`.


## Outcomes and 

Drawing on the integrated results presented in @sec-totalint2, we have identified key insights that underpin our strategies for ongoing evaluation and enhancement:

- **Learning Outcome I** – *Applies comprehensive knowledge in management areas such as finance, strategy, organizational behavior, and marketing to enhance organizational effectiveness and efficiency* - **Course 1218 - Management Accounting**: Improvement plan to be developed.

- **Learning Outcome V** – *Utilizes analytical, critical thinking, and problem-solving skills to navigate challenges and enable lifelong learning within teams and organizations* - **Course: 1312 - Data Analysis and Probability**: Improvement plan to be developed.


# MSc in Economics

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 14

```

## Program objectives

Based on Nova SBE's core values, the program objectives, which were previously defined and submitted to A3ES and international accreditation agencies, have been systematically mapped. This mapping process, as described in @sec-SV, ensures alignment with our institutional ethos and educational goals for the program `{r} print.program.b(c)`.

The @tbl-VO14, below, provides a detailed overview of how these objectives correspond to the learning outcomes, illustrating the integration of Nova SBE’s values into our educational framework:

::: {#tbl-VO14}
```{r echo=FALSE, fig.align='center', out.width="95%"}

VO_table(c)

```

Nova SBE's values and Program objectives for the `{r} print.program.b(c)`
:::

## Learning Outcomes

After evaluating the Program Objectives and their alignment with Nova SBE's core values, and considering the Learning Goals structure outlined in the @sec-PLOS, we have defined the following **Learning Outcomes** for the program `{r} print.program.b(c)`, as detailed in the @tbl-LO14.

::: {#tbl-LO14}
```{r echo=FALSE, fig.align='center', , out.width="98%"}

LO_table(c)

```

Program Learning Outcomes for the `{r} print.program.b(c)`
:::

These Learning Outcomes are described according to the three levels of proficiency defined in @sec-PLOS: Developing, Proficient, and Expert. @tbl-PLO14, below, outlines the levels of proficiency for the Learning Outcomes in the `{r} print.program.b(c)` program. Each Learning Outcome is mapped across three proficiency levels—Developing, Proficient, and Expert—detailing the competencies students are expected to demonstrate as they progress through the program.

::: {#tbl-PLO14}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Prof_table(c)

```

Levels of Proficiency for Learning Outcomes in the `{r} print.program.b(c)`
:::

The defined Learning Outcomes contribute to achieving the program's pre-defined objectives, as detailed in the @tbl-OO14 of the [Appendix 3.A](#sec-app14). Additionally, the specific contributions of individual courses to each Learning Outcome, along with the corresponding levels of proficiency achieved, are detailed in @tbl-CO14, located in [Appendix 3.B](#sec-appcourse14).

## 2023/2024 Academic year

For the academic year 2023/2024, in accordance with the procedure defined in @sec-ALS, the following courses were selected for the Learning Outcomes (LO) assessment process for the `{r} print.program.b(c)` program. The details of these courses and their respective contributions to the LO assessment are presented in the @tbl-ConifgLO14 below.

::: {#tbl-ConifgLO14}
```{r echo=FALSE, fig.align='center', out.width="95%"}

config_table(c)

```

2023/2024 academic year Selected Learning Outcomes and respective courses for the `{r} print.program.b(c)`
:::

## Results

The results for the `{r} print.program.b(c)` for the academic year of 2023/2024, were the following.

### Direct Measures

#### Learning Outcome I:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'I'
e <- FALSE
f <- 2168

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome IV:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'IV'
e <- FALSE
f <- 2188

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```


### Indirect Measures

#### Alumni surveys:

Below, @tbl-KPIalumni14 provides a summary of the alumni survey results for the `{r} print.program.b(c)` during the 2023/2024 academic year. The scores, based on responses from `{r} print.alumni.num(c)` alumni, are reported on an A, B, C, F scale, as outlined in @sec-alumnisurv.

::: {#tbl-KPIalumni14}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Alumni_table (c)

```

Results of the alumni surveys for the `{r} print.program.b(c)`
:::

#### Employers surveys:

The results of the employer survey for the `{r} print.program.b(c)` in the 2023/2024 academic year are summarized in @tbl-KPIemploy14. Based on feedback from `{r} print.employers.num(c)` employers, the scores are presented on an A, B, C, F scale, as detailed in @sec-employsurv.

::: {#tbl-KPIemploy14}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Employer_table (c)

```

Results of the employer surveys for the `{r} print.program.b(c)`
:::

### Integrated assurance overview {#sec-totalint14}

The table below, @tbl-Total14, presents the integrated results for the program `{r} print.program.b(c)`, combining both direct and indirect measures of assessment. Data was triangulated as described in @sec-ALS, ensuring a comprehensive evaluation of the learning outcomes.

::: {#tbl-Total14}
```{r echo=FALSE, fig.align='center', out.width="98%"}

KPI_total_table (c)

```

Integrated direct and indirect measures results for the `{r} print.program.b(c)`
:::

By integrating the various dimensions, including the indirect survey-based data from the 2023/2024 academic year, along with the reassessments and regular assessments from 2023/2024, we gain a comprehensive overview of the learning outcomes for the `{r} print.program.b(c)`.


## Outcomes and Recommendations

Drawing on the integrated results presented in @sec-totalint14, we have identified key insights that underpin our strategies for ongoing evaluation and enhancement:

- **Learning Outcome I** - *Analyses and evaluates national and international economic contexts* – **Course 2168 - Macroeconometrics**: Improvement plan to be developed.

- **Learning Outcome IV** – *Demonstrates effective interpersonal and communication skills to enhance teamwork and collaboration across various settings.* - **Course: 2188 - Microeconomics Analysis**: Improvement plan to be developed.

- **Learning Outcome III** - *Demonstrates proficiency in leveraging core economic principles and techniques to effectively resolve practical economic problems* – Reasons for alumni score should be analyzed.

# MSc in Management

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 15

```

## Program objectives

Based on Nova SBE's core values, the program objectives, which were previously defined and submitted to A3ES and international accreditation agencies, have been systematically mapped. This mapping process, as described in @sec-SV, ensures alignment with our institutional ethos and educational goals for the program `{r} print.program.b(c)`.

The @tbl-VO15, below, provides a detailed overview of how these objectives correspond to the learning outcomes, illustrating the integration of Nova SBE’s values into our educational framework:

::: {#tbl-VO15}
```{r echo=FALSE, fig.align='center', out.width="95%"}

VO_table(c)

```

Nova SBE's values and Program objectives for the `{r} print.program.b(c)`
:::

## Learning Outcomes

After evaluating the Program Objectives and their alignment with Nova SBE's core values, and considering the Learning Goals structure outlined in the @sec-PLOS, we have defined the following **Learning Outcomes** for the program `{r} print.program.b(c)`, as detailed in the @tbl-LO15.

::: {#tbl-LO15}
```{r echo=FALSE, fig.align='center', , out.width="98%"}

LO_table(c)

```

Program Learning Outcomes for the `{r} print.program.b(c)`
:::

These Learning Outcomes are described according to the three levels of proficiency defined in @sec-PLOS: Developing, Proficient, and Expert. @tbl-PLO15, below, outlines the levels of proficiency for the Learning Outcomes in the `{r} print.program.b(c)` program. Each Learning Outcome is mapped across three proficiency levels—Developing, Proficient, and Expert—detailing the competencies students are expected to demonstrate as they progress through the program.

::: {#tbl-PLO15}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Prof_table(c)

```

Levels of Proficiency for Learning Outcomes in the `{r} print.program.b(c)`
:::

The defined Learning Outcomes contribute to achieving the program's pre-defined objectives, as detailed in the @tbl-OO15 of the [Appendix 4.A](#sec-app15). Additionally, the specific contributions of individual courses to each Learning Outcome, along with the corresponding levels of proficiency achieved, are detailed in @tbl-CO15, located in [Appendix 4.B](#sec-appcourse15).

## 2023/2024 Academic year

For the academic year 2023/2024, in accordance with the procedure defined in @sec-ALS, the following courses were selected for the Learning Outcomes (LO) assessment process for the `{r} print.program.b(c)` program. The details of these courses and their respective contributions to the LO assessment are presented in the @tbl-ConifgLO15 below.

::: {#tbl-ConifgLO15}
```{r echo=FALSE, fig.align='center', out.width="95%"}

config_table(c)

```

2023/2024 academic year Selected Learning Outcomes and respective courses for the `{r} print.program.b(c)`
:::

## Results

The results for the `{r} print.program.b(c)` for the academic year of 2023/2024, were the following.

### Direct Measures

#### Learning Outcome I:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'I'
e <- FALSE
f <- 2584

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome IV:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'IV'
e <- FALSE
f <- 2336

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome III - Reassessment 1:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'III'
e <- TRUE
f <- 2414
  
data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome III - Reassessment 2:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'III'
e <- TRUE
f <- 2581
  
data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```


### Indirect Measures

#### Alumni surveys:

Below, @tbl-KPIalumni15 provides a summary of the alumni survey results for the `{r} print.program.b(c)` during the 2023/2024 academic year. The scores, based on responses from `{r} print.alumni.num(c)` alumni, are reported on an A, B, C, F scale, as outlined in @sec-alumnisurv.

::: {#tbl-KPIalumni15}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Alumni_table (c)

```

Results of the alumni surveys for the `{r} print.program.b(c)`
:::

#### Employers surveys:

The results of the employer survey for the `{r} print.program.b(c)` in the 2023/2024 academic year are summarized in @tbl-KPIemploy15. Based on feedback from `{r} print.employers.num(c)` employers, the scores are presented on an A, B, C, F scale, as detailed in @sec-employsurv.

::: {#tbl-KPIemploy15}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Employer_table (c)

```

Results of the employer surveys for the `{r} print.program.b(c)`
:::

### Integrated assurance overview {#sec-totalint15}

The table below, @tbl-Total15, presents the integrated results for the program `{r} print.program.b(c)`, combining both direct and indirect measures of assessment. Data was triangulated as described in @sec-ALS, ensuring a comprehensive evaluation of the learning outcomes.

::: {#tbl-Total15}
```{r echo=FALSE, fig.align='center', out.width="98%"}

KPI_total_table (c)

```

Integrated direct and indirect measures results for the `{r} print.program.b(c)`
:::

By integrating the various dimensions, including the indirect survey-based data from the 2023/2024 academic year, along with the reassessments and regular assessments from 2023/2024, we gain a comprehensive overview of the learning outcomes for the `{r} print.program.b(c)`.


## Outcomes and Recommendations

Drawing on the integrated results presented in @sec-totalint15, no relevant issues were detected, and no specific actions need to be taken at this time. However, Academic Directors should continue their regular monitoring of the program to ensure that the desired learning outcomes are effectively reflected in the program's courses.


# MSc in Finance

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 16

```

## Program objectives

Based on Nova SBE's core values, the program objectives, which were previously defined and submitted to A3ES and international accreditation agencies, have been systematically mapped. This mapping process, as described in @sec-SV, ensures alignment with our institutional ethos and educational goals for the program `{r} print.program.b(c)`.

The @tbl-VO16, below, provides a detailed overview of how these objectives correspond to the learning outcomes, illustrating the integration of Nova SBE’s values into our educational framework:

::: {#tbl-VO16}
```{r echo=FALSE, fig.align='center', out.width="95%"}

VO_table(c)

```

Nova SBE's values and Program objectives for the `{r} print.program.b(c)`
:::

## Learning Outcomes

After evaluating the Program Objectives and their alignment with Nova SBE's core values, and considering the Learning Goals structure outlined in the @sec-PLOS, we have defined the following **Learning Outcomes** for the program `{r} print.program.b(c)`, as detailed in the @tbl-LO16.

::: {#tbl-LO16}
```{r echo=FALSE, fig.align='center', , out.width="98%"}

LO_table(c)

```

Program Learning Outcomes for the `{r} print.program.b(c)`
:::

These Learning Outcomes are described according to the three levels of proficiency defined in @sec-PLOS: Developing, Proficient, and Expert. @tbl-PLO16, below, outlines the levels of proficiency for the Learning Outcomes in the `{r} print.program.b(c)` program. Each Learning Outcome is mapped across three proficiency levels—Developing, Proficient, and Expert—detailing the competencies students are expected to demonstrate as they progress through the program.

::: {#tbl-PLO16}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Prof_table(c)

```

Levels of Proficiency for Learning Outcomes in the `{r} print.program.b(c)`
:::

The defined Learning Outcomes contribute to achieving the program's pre-defined objectives, as detailed in the @tbl-OO16 of the [Appendix 5.A](#sec-app16). Additionally, the specific contributions of individual courses to each Learning Outcome, along with the corresponding levels of proficiency achieved, are detailed in @tbl-CO16, located in [Appendix 5.B](#sec-appcourse16).

## 2023/2024 Academic year

For the academic year 2023/2024, in accordance with the procedure defined in @sec-ALS, the following courses were selected for the Learning Outcomes (LO) assessment process for the `{r} print.program.b(c)` program. The details of these courses and their respective contributions to the LO assessment are presented in the @tbl-ConifgLO16 below.

::: {#tbl-ConifgLO16}
```{r echo=FALSE, fig.align='center', out.width="95%"}

config_table(c)

```

2023/2024 academic year Selected Learning Outcomes and respective courses for the `{r} print.program.b(c)`
:::

## Results

The results for the `{r} print.program.b(c)` for the academic year of 2023/2024, were the following.

### Direct Measures

#### Learning Outcome I:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'I'
e <- FALSE
f <- 2269

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome IV:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'IV'
e <- FALSE
f <- 2270

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```


### Indirect Measures

#### Alumni surveys:

Below, @tbl-KPIalumni16 provides a summary of the alumni survey results for the `{r} print.program.b(c)` during the 2023/2024 academic year. The scores, based on responses from `{r} print.alumni.num(c)` alumni, are reported on an A, B, C, F scale, as outlined in @sec-alumnisurv.

::: {#tbl-KPIalumni16}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Alumni_table (c)

```

Results of the alumni surveys for the `{r} print.program.b(c)`
:::

#### Employers surveys:

The results of the employer survey for the `{r} print.program.b(c)` in the 2023/2024 academic year are summarized in @tbl-KPIemploy16. Based on feedback from `{r} print.employers.num(c)` employers, the scores are presented on an A, B, C, F scale, as detailed in @sec-employsurv.

::: {#tbl-KPIemploy16}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Employer_table (c)

```

Results of the employer surveys for the `{r} print.program.b(c)`
:::

### Integrated assurance overview {#sec-totalint16}

The table below, @tbl-Total16, presents the integrated results for the program `{r} print.program.b(c)`, combining both direct and indirect measures of assessment. Data was triangulated as described in @sec-ALS, ensuring a comprehensive evaluation of the learning outcomes.

::: {#tbl-Total16}
```{r echo=FALSE, fig.align='center', out.width="98%"}

KPI_total_table (c)

```

Integrated direct and indirect measures results for the `{r} print.program.b(c)`
:::

By integrating the various dimensions, including the indirect survey-based data from the 2023/2024 academic year, along with the reassessments and regular assessments from 2023/2024, we gain a comprehensive overview of the learning outcomes for the `{r} print.program.b(c)`.


## Outcomes and Recommendations
Drawing on the integrated results presented in @sec-totalint16, we have identified key insights that underpin our strategies for ongoing evaluation and enhancement:

- **Learning Outcome VI** - *Leverages a deep understanding of sustainability in business and economics to drive ethical transformations and positive outcomes across organizational and project contexts.* – Reasons for alumni score should be analyzed.


# MSc in Business Analytics

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 37

```

## Program objectives

Based on Nova SBE's core values, the program objectives, which were previously defined and submitted to A3ES and international accreditation agencies, have been systematically mapped. This mapping process, as described in @sec-SV, ensures alignment with our institutional ethos and educational goals for the program `{r} print.program.b(c)`.

The @tbl-VO37, below, provides a detailed overview of how these objectives correspond to the learning outcomes, illustrating the integration of Nova SBE’s values into our educational framework:

::: {#tbl-VO37}
```{r echo=FALSE, fig.align='center', out.width="95%"}

VO_table(c)

```

Nova SBE's values and Program objectives for the `{r} print.program.b(c)`
:::

## Learning Outcomes

After evaluating the Program Objectives and their alignment with Nova SBE's core values, and considering the Learning Goals structure outlined in the @sec-PLOS, we have defined the following **Learning Outcomes** for the program `{r} print.program.b(c)`, as detailed in the @tbl-LO37.

::: {#tbl-LO37}
```{r echo=FALSE, fig.align='center', , out.width="98%"}

LO_table(c)

```

Program Learning Outcomes for the `{r} print.program.b(c)`
:::

These Learning Outcomes are described according to the three levels of proficiency defined in @sec-PLOS: Developing, Proficient, and Expert. @tbl-PLO37, below, outlines the levels of proficiency for the Learning Outcomes in the `{r} print.program.b(c)` program. Each Learning Outcome is mapped across three proficiency levels—Developing, Proficient, and Expert—detailing the competencies students are expected to demonstrate as they progress through the program.

::: {#tbl-PLO37}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Prof_table(c)

```

Levels of Proficiency for Learning Outcomes in the `{r} print.program.b(c)`
:::

The defined Learning Outcomes contribute to achieving the program's pre-defined objectives, as detailed in the @tbl-OO37 of the [Appendix 6.A](#sec-app37). Additionally, the specific contributions of individual courses to each Learning Outcome, along with the corresponding levels of proficiency achieved, are detailed in @tbl-CO37, located in [Appendix 6.B](#sec-appcourse37).

## 2023/2024 Academic year

For the academic year 2023/2024, in accordance with the procedure defined in @sec-ALS, the following courses were selected for the Learning Outcomes (LO) assessment process for the `{r} print.program.b(c)` program. The details of these courses and their respective contributions to the LO assessment are presented in the @tbl-ConifgLO37 below.

::: {#tbl-ConifgLO37}
```{r echo=FALSE, fig.align='center', out.width="95%"}

config_table(c)

```

2023/2024 academic year Selected Learning Outcomes and respective courses for the `{r} print.program.b(c)`
:::

## Results

The results for the `{r} print.program.b(c)` for the academic year of 2023/2024, were the following.

### Direct Measures

#### Learning Outcome I:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'I'
e <- FALSE
f <- 2597

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome IV:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'IV'
e <- FALSE
f <- 2607

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome I - Reassessment :

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'I'
e <- TRUE
f <- 2346
  
data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```


### Indirect Measures

#### Alumni surveys:

Below, @tbl-KPIalumni37 provides a summary of the alumni survey results for the `{r} print.program.b(c)` during the 2023/2024 academic year. The scores, based on responses from `{r} print.alumni.num(c)` alumni, are reported on an A, B, C, F scale, as outlined in @sec-alumnisurv.

::: {#tbl-KPIalumni37}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Alumni_table (c)

```

Results of the alumni surveys for the `{r} print.program.b(c)`
:::

#### Employers surveys:

The results of the employer survey for the `{r} print.program.b(c)` in the 2023/2024 academic year are summarized in @tbl-KPIemploy37. Based on feedback from `{r} print.employers.num(c)` employers, the scores are presented on an A, B, C, F scale, as detailed in @sec-employsurv.

::: {#tbl-KPIemploy37}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Employer_table (c)

```

Results of the employer surveys for the `{r} print.program.b(c)`
:::

### Integrated assurance overview {#sec-totalint37}

The table below, @tbl-Total37, presents the integrated results for the program `{r} print.program.b(c)`, combining both direct and indirect measures of assessment. Data was triangulated as described in @sec-ALS, ensuring a comprehensive evaluation of the learning outcomes.

::: {#tbl-Total37}
```{r echo=FALSE, fig.align='center', out.width="98%"}

KPI_total_table (c)

```

Integrated direct and indirect measures results for the `{r} print.program.b(c)`
:::

By integrating the various dimensions, including the indirect survey-based data from the 2023/2024 academic year, along with the reassessments and regular assessments from 2023/2024, we gain a comprehensive overview of the learning outcomes for the `{r} print.program.b(c)`.


## Outcomes and Recommendations
Drawing on the integrated results presented in @sec-totalint37, we have identified key insights that underpin our strategies for ongoing evaluation and enhancement:

- **Learning Outcome VI** - *Leverages a deep understanding of sustainability in business and economics to drive ethical transformations and positive outcomes across organizational and project contexts.* – Reasons for alumni score should be analyzed.


# MSc in Impact Entrepreneurship & Innovation

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 38

```

## Program objectives

Based on Nova SBE's core values, the program objectives, which were previously defined and submitted to A3ES and international accreditation agencies, have been systematically mapped. This mapping process, as described in @sec-SV, ensures alignment with our institutional ethos and educational goals for the program `{r} print.program.b(c)`.

The @tbl-VO38, below, provides a detailed overview of how these objectives correspond to the learning outcomes, illustrating the integration of Nova SBE’s values into our educational framework:

::: {#tbl-VO38}
```{r echo=FALSE, fig.align='center', out.width="95%"}

VO_table(c)

```

Nova SBE's values and Program objectives for the `{r} print.program.b(c)`
:::

## Learning Outcomes

After evaluating the Program Objectives and their alignment with Nova SBE's core values, and considering the Learning Goals structure outlined in the @sec-PLOS, we have defined the following **Learning Outcomes** for the program `{r} print.program.b(c)`, as detailed in the @tbl-LO38.

::: {#tbl-LO38}
```{r echo=FALSE, fig.align='center', , out.width="98%"}

LO_table(c)

```

Program Learning Outcomes for the `{r} print.program.b(c)`
:::

These Learning Outcomes are described according to the three levels of proficiency defined in @sec-PLOS: Developing, Proficient, and Expert. @tbl-PLO38, below, outlines the levels of proficiency for the Learning Outcomes in the `{r} print.program.b(c)` program. Each Learning Outcome is mapped across three proficiency levels—Developing, Proficient, and Expert—detailing the competencies students are expected to demonstrate as they progress through the program.

::: {#tbl-PLO38}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Prof_table(c)

```

Levels of Proficiency for Learning Outcomes in the `{r} print.program.b(c)`
:::

The defined Learning Outcomes contribute to achieving the program's pre-defined objectives, as detailed in the @tbl-OO38 of the [Appendix 7.A](#sec-app38). Additionally, the specific contributions of individual courses to each Learning Outcome, along with the corresponding levels of proficiency achieved, are detailed in @tbl-CO38, located in [Appendix 7.B](#sec-appcourse38).

## 2023/2024 Academic year

For the academic year 2023/2024, in accordance with the procedure defined in @sec-ALS, the following courses were selected for the Learning Outcomes (LO) assessment process for the `{r} print.program.b(c)` program. The details of these courses and their respective contributions to the LO assessment are presented in the @tbl-ConifgLO38 below.

::: {#tbl-ConifgLO38}
```{r echo=FALSE, fig.align='center', out.width="95%"}

config_table(c)

```

2023/2024 academic year Selected Learning Outcomes and respective courses for the `{r} print.program.b(c)`
:::

## Results

The results for the `{r} print.program.b(c)` for the academic year of 2023/2024, were the following.

### Direct Measures

#### Learning Outcome I:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'I'
e <- FALSE
f <- 2628

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome IV:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'IV'
e <- FALSE
f <- 2710

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```


### Indirect Measures

#### Alumni surveys:

Below, @tbl-KPIalumni38 provides a summary of the alumni survey results for the `{r} print.program.b(c)` during the 2023/2024 academic year. The scores, based on responses from `{r} print.alumni.num(c)` alumni, are reported on an A, B, C, F scale, as outlined in @sec-alumnisurv.

::: {#tbl-KPIalumni38}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Alumni_table (c)

```

Results of the alumni surveys for the `{r} print.program.b(c)`
:::

#### Employers surveys:

The results of the employer survey for the `{r} print.program.b(c)` in the 2023/2024 academic year are summarized in @tbl-KPIemploy38. Based on feedback from `{r} print.employers.num(c)` employers, the scores are presented on an A, B, C, F scale, as detailed in @sec-employsurv.

::: {#tbl-KPIemploy38}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Employer_table (c)

```

Results of the employer surveys for the `{r} print.program.b(c)`
:::

### Integrated assurance overview {#sec-totalint38}

The table below, @tbl-Total38, presents the integrated results for the program `{r} print.program.b(c)`, combining both direct and indirect measures of assessment. Data was triangulated as described in @sec-ALS, ensuring a comprehensive evaluation of the learning outcomes.

::: {#tbl-Total38}
```{r echo=FALSE, fig.align='center', out.width="98%"}

KPI_total_table (c)

```

Integrated direct and indirect measures results for the `{r} print.program.b(c)`
:::

By integrating the various dimensions, including the indirect survey-based data from the 2023/2024 academic year, along with the reassessments and regular assessments from 2023/2024, we gain a comprehensive overview of the learning outcomes for the `{r} print.program.b(c)`.


## Outcomes and Recommendations
Drawing on the integrated results presented in @sec-totalint38, we have identified key insights that underpin our strategies for ongoing evaluation and enhancement:

- **Learning Outcome I** - *Utilizes a deep understanding of market trends and societal demands to craft actionable and innovative strategies that address these needs.* – Reasons for employer score should be analyzed.


# MSc in InternationalDevelopment and Public Policy

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 39

```

## Program objectives

Based on Nova SBE's core values, the program objectives, which were previously defined and submitted to A3ES and international accreditation agencies, have been systematically mapped. This mapping process, as described in @sec-SV, ensures alignment with our institutional ethos and educational goals for the program `{r} print.program.b(c)`.

The @tbl-VO39, below, provides a detailed overview of how these objectives correspond to the learning outcomes, illustrating the integration of Nova SBE’s values into our educational framework:

::: {#tbl-VO39}
```{r echo=FALSE, fig.align='center', out.width="95%"}

VO_table(c)

```

Nova SBE's values and Program objectives for the `{r} print.program.b(c)`
:::

## Learning Outcomes

After evaluating the Program Objectives and their alignment with Nova SBE's core values, and considering the Learning Goals structure outlined in the @sec-PLOS, we have defined the following **Learning Outcomes** for the program `{r} print.program.b(c)`, as detailed in the @tbl-LO39.

::: {#tbl-LO39}
```{r echo=FALSE, fig.align='center', , out.width="98%"}

LO_table(c)

```

Program Learning Outcomes for the `{r} print.program.b(c)`
:::

These Learning Outcomes are described according to the three levels of proficiency defined in @sec-PLOS: Developing, Proficient, and Expert. @tbl-PLO39, below, outlines the levels of proficiency for the Learning Outcomes in the `{r} print.program.b(c)` program. Each Learning Outcome is mapped across three proficiency levels—Developing, Proficient, and Expert—detailing the competencies students are expected to demonstrate as they progress through the program.

::: {#tbl-PLO39}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Prof_table(c)

```

Levels of Proficiency for Learning Outcomes in the `{r} print.program.b(c)`
:::

The defined Learning Outcomes contribute to achieving the program's pre-defined objectives, as detailed in the @tbl-OO39 of the [Appendix 8.A](#sec-app39). Additionally, the specific contributions of individual courses to each Learning Outcome, along with the corresponding levels of proficiency achieved, are detailed in @tbl-CO39, located in [Appendix 8.B](#sec-appcourse39).

## 2023/2024 Academic year

For the academic year 2023/2024, in accordance with the procedure defined in @sec-ALS, the following courses were selected for the Learning Outcomes (LO) assessment process for the `{r} print.program.b(c)` program. The details of these courses and their respective contributions to the LO assessment are presented in the @tbl-ConifgLO39 below.

::: {#tbl-ConifgLO39}
```{r echo=FALSE, fig.align='center', out.width="95%"}

config_table(c)

```

2023/2024 academic year Selected Learning Outcomes and respective courses for the `{r} print.program.b(c)`
:::

## Results

The results for the `{r} print.program.b(c)` for the academic year of 2023/2024, were the following.

### Direct Measures

#### Learning Outcome I:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'I'
e <- FALSE
f <- 2742

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome IV:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'IV'
e <- FALSE
f <- 2739

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome I - Reassessment :

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'I'
e <- TRUE
f <- 2746
  
data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```


### Indirect Measures

#### Alumni surveys:

Below, @tbl-KPIalumni39 provides a summary of the alumni survey results for the `{r} print.program.b(c)` during the 2023/2024 academic year. The scores, based on responses from `{r} print.alumni.num(c)` alumni, are reported on an A, B, C, F scale, as outlined in @sec-alumnisurv.

::: {#tbl-KPIalumni39}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Alumni_table (c)

```

Results of the alumni surveys for the `{r} print.program.b(c)`
:::

#### Employers surveys:

The results of the employer survey for the `{r} print.program.b(c)` in the 2023/2024 academic year are summarized in @tbl-KPIemploy39. Based on feedback from `{r} print.employers.num(c)` employers, the scores are presented on an A, B, C, F scale, as detailed in @sec-employsurv.

::: {#tbl-KPIemploy39}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Employer_table (c)

```

Results of the employer surveys for the `{r} print.program.b(c)`
:::

### Integrated assurance overview {#sec-totalint39}

The table below, @tbl-Total39, presents the integrated results for the program `{r} print.program.b(c)`, combining both direct and indirect measures of assessment. Data was triangulated as described in @sec-ALS, ensuring a comprehensive evaluation of the learning outcomes.

::: {#tbl-Total39}
```{r echo=FALSE, fig.align='center', out.width="98%"}

KPI_total_table (c)

```

Integrated direct and indirect measures results for the `{r} print.program.b(c)`
:::

By integrating the various dimensions, including the indirect survey-based data from the 2023/2024 academic year, along with the reassessments and regular assessments from 2023/2024, we gain a comprehensive overview of the learning outcomes for the `{r} print.program.b(c)`.


## Outcomes and Recommendations
Drawing on the integrated results presented in @sec-totalint39, we have identified key insights that underpin our strategies for ongoing evaluation and enhancement:

- **Learning Outcome I** - *Applies understanding of the institutional framework, including its constraints and historical economic influences, to navigate and influence policy decisions.* – **Course 2746 - Public Policy I**: Improvement plan to be developed.

- **Learning Outcome I** - *Applies understanding of the institutional framework, including its constraints and historical economic influences, to navigate and influence policy decisions.*: Reasons for alumni score should be analyzed

# PhD in Economics and Finance

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 27

```

## Program objectives

Based on Nova SBE's core values, the program objectives, which were previously defined and submitted to A3ES and international accreditation agencies, have been systematically mapped. This mapping process, as described in @sec-SV, ensures alignment with our institutional ethos and educational goals for the program `{r} print.program.b(c)`.

The @tbl-VO27, below, provides a detailed overview of how these objectives correspond to the learning outcomes, illustrating the integration of Nova SBE’s values into our educational framework:

::: {#tbl-VO27}
```{r echo=FALSE, fig.align='center', out.width="95%"}

VO_table(c)

```

Nova SBE's values and Program objectives for the `{r} print.program.b(c)`
:::

## Learning Outcomes

After evaluating the Program Objectives and their alignment with Nova SBE's core values, and considering the Learning Goals structure outlined in the @sec-PLOS, we have defined the following **Learning Outcomes** for the program `{r} print.program.b(c)`, as detailed in the @tbl-LO27.

::: {#tbl-LO27}
```{r echo=FALSE, fig.align='center', , out.width="98%"}

LO_table(c)

```

Program Learning Outcomes for the `{r} print.program.b(c)`
:::

These Learning Outcomes are described according to the three levels of proficiency defined in @sec-PLOS: Developing, Proficient, and Expert. @tbl-PLO27, below, outlines the levels of proficiency for the Learning Outcomes in the `{r} print.program.b(c)` program. Each Learning Outcome is mapped across three proficiency levels—Developing, Proficient, and Expert—detailing the competencies students are expected to demonstrate as they progress through the program.

::: {#tbl-PLO27}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Prof_table(c)

```

Levels of Proficiency for Learning Outcomes in the `{r} print.program.b(c)`
:::

The defined Learning Outcomes contribute to achieving the program's pre-defined objectives, as detailed in the @tbl-OO27 of the [Appendix 9.A](#sec-app27). Additionally, the specific contributions of individual courses to each Learning Outcome, along with the corresponding levels of proficiency achieved, are detailed in @tbl-CO27, located in [Appendix 9.B](#sec-appcourse27).

## 2023/2024 Academic year

For the academic year 2023/2024, in accordance with the procedure defined in @sec-ALS, the following courses were selected for the Learning Outcomes (LO) assessment process for the `{r} print.program.b(c)` program. The details of these courses and their respective contributions to the LO assessment are presented in the @tbl-ConifgLO27 below.

::: {#tbl-ConifgLO27}
```{r echo=FALSE, fig.align='center', out.width="95%"}

config_table(c)

```

2023/2024 academic year Selected Learning Outcomes and respective courses for the `{r} print.program.b(c)`
:::

## Results

The results for the `{r} print.program.b(c)` for the academic year of 2023/2024, were the following.

### Direct Measures

#### Learning Outcome I:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'I'
e <- FALSE
f <- 6109

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome IV:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'IV'
e <- FALSE
f <- 6124

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome II - Reassessment :

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'II'
e <- TRUE
f <- 6101
  
data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome V - Reassessment :

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'V'
e <- TRUE
f <- 6121
  
data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```


### Indirect Measures

#### Alumni surveys:

Below, @tbl-KPIalumni27 provides a summary of the alumni survey results for the `{r} print.program.b(c)` during the 2023/2024 academic year. The scores, based on responses from `{r} print.alumni.num(c)` alumni, are reported on an A, B, C, F scale, as outlined in @sec-alumnisurv.

::: {#tbl-KPIalumni27}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Alumni_table (c)

```

Results of the alumni surveys for the `{r} print.program.b(c)`
:::

#### Employers surveys:

The results of the employer survey for the `{r} print.program.b(c)` are not available for the academic year 2023/24. Given the small batch of graduates each year and the fragmented universe of employers, it was not possible to gather sufficient data during this period.


### Integrated assurance overview {#sec-totalint27}

The table below, @tbl-Total27, presents the integrated results for the program `{r} print.program.b(c)`, combining both direct and indirect measures of assessment. Data was triangulated as described in @sec-ALS, ensuring a comprehensive evaluation of the learning outcomes.

::: {#tbl-Total27}
```{r echo=FALSE, fig.align='center', out.width="98%"}

KPI_total_table (c)

```

Integrated direct and indirect measures results for the `{r} print.program.b(c)`
:::

By integrating the various dimensions, including the indirect survey-based data from the 2023/2024 academic year, along with the reassessments and regular assessments from 2023/2024, we gain a comprehensive overview of the learning outcomes for the `{r} print.program.b(c)`.


## Outcomes and Recommendations
Drawing on the integrated results presented in @sec-totalint27, we have identified key insights that underpin our strategies for ongoing evaluation and enhancement:

- **Learning Outcome II** - *Applies research concepts and tools* – **Course 6101 - Microeconomic Theory I**: Improvement plan to be developed.


# PhD in Management

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 33

```

## Program objectives

Based on Nova SBE's core values, the program objectives, which were previously defined and submitted to A3ES and international accreditation agencies, have been systematically mapped. This mapping process, as described in @sec-SV, ensures alignment with our institutional ethos and educational goals for the program `{r} print.program.b(c)`.

The @tbl-VO33, below, provides a detailed overview of how these objectives correspond to the learning outcomes, illustrating the integration of Nova SBE’s values into our educational framework:

::: {#tbl-VO33}
```{r echo=FALSE, fig.align='center', out.width="95%"}

VO_table(c)

```

Nova SBE's values and Program objectives for the `{r} print.program.b(c)`
:::

## Learning Outcomes

After evaluating the Program Objectives and their alignment with Nova SBE's core values, and considering the Learning Goals structure outlined in the @sec-PLOS, we have defined the following **Learning Outcomes** for the program `{r} print.program.b(c)`, as detailed in the @tbl-LO33.

::: {#tbl-LO33}
```{r echo=FALSE, fig.align='center', , out.width="98%"}

LO_table(c)

```

Program Learning Outcomes for the `{r} print.program.b(c)`
:::

These Learning Outcomes are described according to the three levels of proficiency defined in @sec-PLOS: Developing, Proficient, and Expert. @tbl-PLO33, below, outlines the levels of proficiency for the Learning Outcomes in the `{r} print.program.b(c)` program. Each Learning Outcome is mapped across three proficiency levels—Developing, Proficient, and Expert—detailing the competencies students are expected to demonstrate as they progress through the program.

::: {#tbl-PLO33}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Prof_table(c)

```

Levels of Proficiency for Learning Outcomes in the `{r} print.program.b(c)`
:::

The defined Learning Outcomes contribute to achieving the program's pre-defined objectives, as detailed in the @tbl-OO33 of the [Appendix 10.A](#sec-app33). Additionally, the specific contributions of individual courses to each Learning Outcome, along with the corresponding levels of proficiency achieved, are detailed in @tbl-CO33, located in [Appendix 10.B](#sec-appcourse33).

## 2023/2024 Academic year

For the academic year 2023/2024, in accordance with the procedure defined in @sec-ALS, the following courses were selected for the Learning Outcomes (LO) assessment process for the `{r} print.program.b(c)` program. The details of these courses and their respective contributions to the LO assessment are presented in the @tbl-ConifgLO33 below.

::: {#tbl-ConifgLO33}
```{r echo=FALSE, fig.align='center', out.width="95%"}

config_table(c)

```

2023/2024 academic year Selected Learning Outcomes and respective courses for the `{r} print.program.b(c)`
:::

## Results

The results for the `{r} print.program.b(c)` for the academic year of 2023/2024, were the following.

### Direct Measures

#### Learning Outcome I:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'I'
e <- FALSE
f <- 6202

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```

#### Learning Outcome IV:

```{r echo=FALSE, warning = FALSE, message = FALSE}

d <- 'IV'
e <- FALSE
f <- 6214

data.course.outcome(c,d,e,f)

```

`{r} print.outcome(c,d)`

**Course assessed**: `{r} print.course(c,d,e,f)`

**Assessment moment**: `{r} print.assessment(c,d,e,f)`

```{r echo=FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width = '60%', fig.asp=0.4}
plot(p)

```

```{r echo=FALSE, warning = FALSE, message = FALSE,  fig.align='center', out.width="60%"}
plot(OR_table)

```



### Indirect Measures

#### Alumni surveys:

Below, @tbl-KPIalumni33 provides a summary of the alumni survey results for the `{r} print.program.b(c)` during the 2023/2024 academic year. The scores, based on responses from `{r} print.alumni.num(c)` alumni, are reported on an A, B, C, F scale, as outlined in @sec-alumnisurv.

::: {#tbl-KPIalumni33}
```{r echo=FALSE, fig.align='center', out.width="98%"}

Alumni_table (c)

```

Results of the alumni surveys for the `{r} print.program.b(c)`
:::

#### Employers surveys:

The results of the employer survey for the `{r} print.program.b(c)` are not available for the academic year 2023/24. Given the small batch of graduates each year and the fragmented universe of employers, it was not possible to gather sufficient data during this period.


### Integrated assurance overview {#sec-totalint33}

The table below, @tbl-Total33, presents the integrated results for the program `{r} print.program.b(c)`, combining both direct and indirect measures of assessment. Data was triangulated as described in @sec-ALS, ensuring a comprehensive evaluation of the learning outcomes.

::: {#tbl-Total33}
```{r echo=FALSE, fig.align='center', out.width="98%"}

KPI_total_table (c)

```

Integrated direct and indirect measures results for the `{r} print.program.b(c)`
:::

By integrating the various dimensions, including the indirect survey-based data from the 2023/2024 academic year, along with the reassessments and regular assessments from 2023/2024, we gain a comprehensive overview of the learning outcomes for the `{r} print.program.b(c)`.


## Outcomes and Recommendations
Drawing on the integrated results presented in @sec-totalint33, we have identified key insights that underpin our strategies for ongoing evaluation and enhancement:

- **Learning Outcome VI** - *Leverages a deep understanding of sustainability in business and economics to drive ethical transformations and positive outcomes across organizational and project contexts.* – Reasons for alumni score should be analyzed


# Final Recommendations and future developments

2023/2024 marks the end of the first three-year cycle. This initial approach to AoL allowed us to gain important insights not only into the programs, but also into the AoL process itself.

Over these three years, results were generally positive; however, some issues were identified that prompted the implementation of improvement actions by course-responsible faculty, with the support of academic directors. These first three years also enabled the faculty to develop a deeper understanding of the learning outcomes and how they should be reflected in the curriculum.

Nonetheless, several key limitations remain in the current AoL process, including:

- **Lack of LO-Specific Assessment Moments**: In many courses, the existing assessment framework does not offer the granularity needed to align directly with each learning outcome, leading to a reliance on broader, less targeted proxy evaluations.

- **Manual and Time-Consuming Processes**: The current approach for selecting learning outcomes, identifying courses, choosing assessment moments, and gathering data is predominantly manual, labor-intensive, and time-consuming. This restricts the overall throughput of the AoL process, limiting its agility and the ability to promptly address identified issues.

- **Difficulty Interpreting and Reflecting LOs**: Faculty can at times find challenging to clearly interpret learning outcomes and effectively integrate them into the curriculum, which can lead to a misalignment between the intended objectives and course content.

In the next three-year cycle, starting in 2024/2025, we plan to leverage our insights from this initial period to implement strategic improvements across the AoL process. These actions aim to enhance the precision of assessments, streamline data collection, and ensure that learning outcomes are clearly defined and effectively integrated into course content. Our key initiatives include:

- **Align Assessment with Learning Outcomes**: Encourage faculty to develop dedicated assessment moments that directly correspond to each learning outcome, ensuring a more precise evaluation of competency acquisition.

- **Launch of the AoLApp**: To address the manual and time-consuming aspects of the current AoL process, we are launching the AoLApp. Integrated into the already existing online FacultyApp, it will streamline data collection, facilitate seamless interaction between faculty and Academic Directors, and enable the recording of LO-specific improvement plans, thereby enhancing overall efficiency and responsiveness.

- **Review and Simplification of Learning Outcomes**: With the support of academic directors, review the program learning outcomes to simplify the statements, ensure clarity and coherence with the current logic, and align them with Bloom's Taxonomy.

- **Pre-load Existing LO Mapping**: Pre-load the current learning outcomes mapping into the course syllabus and provide faculty with the option to adjust the mapping to better reflect the actual course content. This aims to improve faculty awareness of each program's LOs and ensure a greater alignment between the desired outcomes and course content.

These initiatives demonstrate our commitment to continuous improvement and excellence, aiming to create a more agile, responsive, and effective AoL process that fully supports our community. Moving forward, we remain dedicated to supporting both faculty and students in achieving their full potential through a clearer, more integrated approach to learning outcomes and curriculum development.


\newpage

# Appendices {.unnumbered .appendix}

```{=latex}
\newpage
\landscape
\pagestyle{landscapeplain}
```

## Appendix 1.A {#sec-app1 .unnumbered .appendix}

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 1

```

::: {#tbl-OO1}
```{r echo=FALSE, fig.align='center', out.width="98%"}

OO_table(c)

```

Learning Outcomes and Program Objectives for `{r} print.program.b(c)`
:::

\newpage

## Appendix 1.B {#sec-appcourse1 .unnumbered .appendix}

::: {#tbl-CO1}
```{r echo=FALSE, fig.align='center', out.width="98%"}

CO_table(c)

```

Mapping of Course Proficiency Levels to Learning Outcomes for `{r} print.program.b(c)`
:::

\newpage

## Appendix 2.A {#sec-app2 .unnumbered .appendix}

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 2

```

::: {#tbl-OO2}
```{r echo=FALSE, fig.align='center', out.width="98%"}

OO_table(c)

```

Learning Outcomes and Program Objectives for `{r} print.program.b(c)`
:::

\newpage

## Appendix 2.B {#sec-appcourse2 .unnumbered .appendix}

::: {#tbl-CO2}
```{r echo=FALSE, fig.align='center', out.width="98%"}

CO_table(c)

```

Mapping of Course Proficiency Levels to Learning Outcomes for `{r} print.program.b(c)`
:::

\newpage

## Appendix 3.A {#sec-app14 .unnumbered .appendix}

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 14

```

::: {#tbl-OO14}
```{r echo=FALSE, fig.align='center', out.width="98%"}

OO_table(c)

```

Learning Outcomes and Program Objectives for `{r} print.program.b(c)`
:::

\newpage

## Appendix 3.B {#sec-appcourse14 .unnumbered .appendix}

::: {#tbl-CO14}
```{r echo=FALSE, fig.align='center', out.width="98%"}

CO_table(c)

```

Mapping of Course Proficiency Levels to Learning Outcomes for `{r} print.program.b(c)`
:::

\newpage

## Appendix 4.A {#sec-app15 .unnumbered .appendix}

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 15

```

::: {#tbl-OO15}
```{r echo=FALSE, fig.align='center', out.width="98%"}

OO_table(c)

```

Learning Outcomes and Program Objectives for `{r} print.program.b(c)`
:::

\newpage

## Appendix 4.B {#sec-appcourse15 .unnumbered .appendix}

::: {#tbl-CO15}
```{r echo=FALSE, fig.align='center', out.width="98%"}

CO_table(c)

```

Mapping of Course Proficiency Levels to Learning Outcomes for `{r} print.program.b(c)`
:::

\newpage


## Appendix 5.A {#sec-app16 .unnumbered .appendix}

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 16

```

::: {#tbl-OO16}
```{r echo=FALSE, fig.align='center', out.width="98%"}

OO_table(c)

```

Learning Outcomes and Program Objectives for `{r} print.program.b(c)`
:::

\newpage

## Appendix 5.B {#sec-appcourse16 .unnumbered .appendix}

::: {#tbl-CO16}
```{r echo=FALSE, fig.align='center', out.width="98%"}

CO_table(c)

```

Mapping of Course Proficiency Levels to Learning Outcomes for `{r} print.program.b(c)`
:::

\newpage


## Appendix 6.A {#sec-app37 .unnumbered .appendix}

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 37

```

::: {#tbl-OO37}
```{r echo=FALSE, fig.align='center', out.width="98%"}

OO_table(c)

```

Learning Outcomes and Program Objectives for `{r} print.program.b(c)`
:::

\newpage

## Appendix 6.B {#sec-appcourse37 .unnumbered .appendix}

::: {#tbl-CO37}
```{r echo=FALSE, fig.align='center', out.width="98%"}

CO_table(c)

```

Mapping of Course Proficiency Levels to Learning Outcomes for `{r} print.program.b(c)`
:::

\newpage

## Appendix 7.A {#sec-app38 .unnumbered .appendix}

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 38

```

::: {#tbl-OO38}
```{r echo=FALSE, fig.align='center', out.width="98%"}

OO_table(c)

```

Learning Outcomes and Program Objectives for `{r} print.program.b(c)`
:::

\newpage

## Appendix 7.B {#sec-appcourse38 .unnumbered .appendix}

::: {#tbl-CO38}
```{r echo=FALSE, fig.align='center', out.width="98%"}

CO_table(c)

```

Mapping of Course Proficiency Levels to Learning Outcomes for `{r} print.program.b(c)`
:::

\newpage

## Appendix 8.A {#sec-app39 .unnumbered .appendix}

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 39

```

::: {#tbl-OO39}
```{r echo=FALSE, fig.align='center', out.width="98%"}

OO_table(c)

```

Learning Outcomes and Program Objectives for `{r} print.program.b(c)`
:::

\newpage

## Appendix 8.B {#sec-appcourse39 .unnumbered .appendix}

::: {#tbl-CO39}
```{r echo=FALSE, fig.align='center', out.width="98%"}

CO_table(c)

```

Mapping of Course Proficiency Levels to Learning Outcomes for `{r} print.program.b(c)`
:::

\newpage

## Appendix 9.A {#sec-app27 .unnumbered .appendix}

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 27

```

::: {#tbl-OO27}
```{r echo=FALSE, fig.align='center', out.width="98%"}

OO_table(c)

```

Learning Outcomes and Program Objectives for `{r} print.program.b(c)`
:::

\newpage

## Appendix 9.B {#sec-appcourse27 .unnumbered .appendix}

::: {#tbl-CO27}
```{r echo=FALSE, fig.align='center', out.width="98%"}

CO_table(c)

```

Mapping of Course Proficiency Levels to Learning Outcomes for `{r} print.program.b(c)`
:::

\newpage

## Appendix 10.A {#sec-app33 .unnumbered .appendix}

```{r echo=FALSE, warning = FALSE, message = FALSE}

c <- 33

```

::: {#tbl-OO33}
```{r echo=FALSE, fig.align='center', out.width="98%"}

OO_table(c)

```

Learning Outcomes and Program Objectives for `{r} print.program.b(c)`
:::

\newpage

## Appendix 10.B {#sec-appcourse33 .unnumbered .appendix}

::: {#tbl-CO33}
```{r echo=FALSE, fig.align='center', out.width="98%"}

CO_table(c)

```

Mapping of Course Proficiency Levels to Learning Outcomes for `{r} print.program.b(c)`
:::
